---
title: "Shiny Docker Guide"
output: html_document
date: "2025-09-05"
editor_options: 
  chunk_output_type: console
---

Files in the folder app:
app.R #shniy app
data #folder with data
start.command #for MAC
start.bat #for windows
docker-compose.yml
Dockerfile
.dockerignire

Install the libraries and make sure the app in working
```{r}
setwd('~/google_drive_uchicago/ImmgenT/analysis/data_integration/IGT1_96/immgenT_Apps/immgent_app1/')
library(shiny)
library(Seurat)
library(ggplot2)
library(dplyr)
library(DT)

shiny::runApp("app.R", launch.browser = TRUE)

```

Color from
```{r}
library(ZemmourLib)
write.table(data.frame(level2 = names(ZemmourLib::immgent_colors$level2), color = ZemmourLib::immgent_colors$level2), file = "annotation_level2_colors.csv", row.names = F, sep = ",")
```


**Build Docker container**
1. Install Docker Desktop
2. Local Build with compose (recommended): first time take a lot of time. BUILDS what is called an IMAGE (a template)
```{bash}
cd ~/google_drive_uchicago/ImmgenT/analysis/data_integration/IGT1_96/immgenT_Apps/immgent_app1/ 
#docker build --no-cache -t immgent-app1 .
docker compose build --no-cache
```
3. create/Run the app --> what is called a CONTAINER
```{bash}
docker compose up #--force-recreate
```
Then visit: <http://localhost:3838/app/>

For next times: Double-click:
- macOS: double-click `start.command`
- Windows: double-click `start.bat`

Stop it
- If using compose: press `Ctrl + C` in that terminal (or `docker compose down`).
- If using `docker run`: `Ctrl + C` stops the container.

5. Build the arm64 version, faster and doesn't use shiny server that only works with amd64.
a. first need Dockerfile.arm64
b. Buid image and Create container
```{bash}
docker build --platform linux/arm64 -f Dockerfile.arm64 -t immgent_app1:0.2.arm64 .
docker run -d --name immgent_app1_arm64 -p 3838:3838 -v "$PWD/data":/app/data immgent_app1:0.2.arm64
```

6. best to share offline (docker hub gave be trouble?)
in a folder named immgent_app1: add the saved tar image + code to run the image (open_mac.command and open_windows.bat+run_windows.ps1)+ README
```{bash}
docker save immgent_app1:0.2.arm64 -o immgent_app1_0.2.arm64.tar
```

compress all
```{bash}
tar -czf immgent_app1.tar.gz immgent_app1/
```


**Update after code changes**

```{bash}
docker compose build && docker compose up
```

**Tips & Troubleshooting**

Validate your compose file after edits:
```{bash}
docker compose config
docker compose ps #Confirm the new container is running
docker compose logs -f
docker images #lists images
docker ps #lists containers

```

**Sharing on Docker Hub**
1. Create a Docker Hub repo (public)
2. 
```{bash}
cd appfolder
docker build --platform=linux/amd64 -t dzemmour/immgent_app1:0.1 .

#doesn't work Optional but recommended for Apple Silicon + Windows users) build a multi-arch image so it runs natively on both Intel/AMD and M1/M2
docker buildx create --use
docker buildx build --platform linux/amd64,linux/arm64 -t dzemmour/immgent_app1:0.1 --push .

#Optionally also tag :latest and push it so users can just pull the default
docker tag dzemmour/immgent_app1:0.1 dzemmour/immgent_app1:latest
docker push dzemmour/immgent_app1:latest


# users run:
# docker run --rm -p 3838:3838 yourdockerhub/immgent-app1:latest
```

**Version with arm64 tag**
RShniy server only works with AMD64 --> build doesn't use RShiny Server but just RShiny --> a few differences on how packages are installed and the dirwctory for data
1. first need Dockerfile.arm64 
2. local build
```{bash}
# On an M1/M2/M3 Mac, this will default to arm64; you can be explicit:
#docker build --platform linux/arm64 -f Dockerfile.arm64 -t dzemmour/immgent_app1:arm64 . -->
docker build --platform linux/arm64 -f Dockerfile.arm64 -t immgent_app1:0.2.arm64 .
```
3. Run
```{bash}
#docker run -d --name immgent-app1-arm -p 3838:3838 -v "$PWD/data":/app/data dzemmour/immgent_app1:arm64
docker run -d --name immgent_app1_arm64 -p 3838:3838 -v "$PWD/data":/app/data immgent_app1:0.2.arm64
# then visit http://localhost:3838

```

publish the arm tag
```{bash}
docker login
docker images
docker tag dzemmour/immgent_app1:arm64 dzemmour/immgent_app1:latestarm64
docker push dzemmour/immgent_app1:latestarm64
```

**Sharing the image Offline**

Save image
```{bash}
docker compose images
docker images
# use the EXACT repo:tag you want
docker save immgent_app1-app:latest -o immgent_app1-app_latest.tar
#docker save immgent_app1:0.2.arm64 -o immgent_app1_0.2.arm64.tar
```
on target machine of a colleague
1. install Docker Desktop
2. load the app
```{bash}
docker load -i immgent_app1-app_latest.tar
docker run --rm -p 3838:3838 immgent_app1-app:latest
```

**TIPS**
- Large data / memory: Increase Docker Desktop memory (Preferences → Resources) if loading huge objects.
- Port already in use: Change the left side of `-p 3838:3838` to another number, e.g., `-p 8080:3838` and open <http://localhost:8080/app/>.
- Linux users: Replace `open` (macOS) with `xdg-open` if you create a launcher.
