---
title: "RShiny"
output: html_document
date: "2025-09-05"
editor_options: 
  chunk_output_type: console
---

```{r}
install.packages(c("rsconnect", "shiny", "Seurat", "dplyr", "ggplot2", "DT"))
# Optional but recommended for reproducible deployments:
install.packages("renv")

libs = c("rsconnect", "shiny", "Seurat", "dplyr", "ggplot2", "DT", "renv") 
sapply(libs, function(x) suppressMessages(suppressWarnings(library(x, character.only = TRUE, quietly = T, warn.conflicts  = F))))

setwd('/Users/david/Library/CloudStorage/GoogleDrive-zemmour@uchicago.edu/My Drive/ImmgenT/analysis/data_integration/IGT1_96/immgenT_Apps/immgent_app1/Rshiny_deployment/immgent_app1/')


```

Connect your shinyapps.io account (copy token and secret from the shinyapps.io dashboard → Tokens):

```{r}
library(rsconnect) 
# EITHER interactive:
# rsconnect::connectUser()   # opens a browser, pastes token/secret for you

# OR non-interactive:
# rsconnect::setAccountInfo(name = "<your-account>", token = "<TOKEN>", secret = "<SECRET>")
rsconnect::setAccountInfo(name='davidpz', token='1B804256A96E2B32EC55AB4B61F1EA4F', secret='RcRond8aP/UmIYbKPvoZXGSORtS18emhHXT36ees')

```

(Official quick-start docs: deploy from IDE “Publish” button or deployApp() API.

2) Prepare your app folder

Create a folder, e.g. Treg_App/, with your app.R only (don’t put giant .rds data in here; users will upload at runtime).

Optional: lock your package versions so Posit’s build servers install exactly what you use locally:

```{r}
# in the app folder
renv::init()
renv::snapshot()

```

3) Make your app upload-friendly & disk-backed

You already set options(shiny.maxRequestSize = ...) at the top of your app.R — good. Shiny’s default is only 5 MB, so this is required for large .rds uploads.

4) Deploy

From R in the parent directory that contains immgenT_App1/:
```{r}
library(rsconnect)
setwd("/Users/david/Library/CloudStorage/GoogleDrive-zemmour@uchicago.edu/My Drive/ImmgenT/analysis/data_integration/IGT1_96/immgenT_Apps/immgent_app1/Rshiny_deployment")
rsconnect::deployApp(appDir = "immgent_app1", appName = "immgenT_App1")

```

5) Pick an instance size that fits your data

On shinyapps.io (dashboard → your app → Settings → Instance Size), choose enough RAM for Seurat with uploads. Defaults are typically 1 GB (“large”). You can raise to 2 GB, 4 GB, 8 GB depending on your plan. 

6) Mind these platform limits

Bundle (deploy) size: the uploaded app bundle must be ≤ 1 GB on Free/Starter; up to 5 GB on higher plans. Don’t include your big .rds in the repo—have users upload it at runtime. 

Upload size at runtime: governed by options(shiny.maxRequestSize=...) in your app. (Default 5 MB; raise as needed.) 

**After the first deploy, you can just re-run deployApp() to update.**

When you do need to touch renv
. You changed repositories (e.g., added an R-universe for BPCells). Make sure that repo line is present in your app (e.g., .Rprofile) and then renv::snapshot() so the build server knows where to install from.
. You added/removed/updated packages (e.g., started using BPCells, SeuratDisk, etc.).
Install them in your app’s renv:
```{r}
setwd("/Users/david/Desktop/immgenT_Apps/")
renv::install("BPCells")  # example
renv::snapshot() #Snapshot to refresh renv.lock
rsconnect::deployApp("immgenT_App1") 
rsconnect::deployApp(appDir = "immgenT_App1", appName = "immgenT_App1") #Redeploy
```

if you only changed files (R code, UI, small assets) and didn’t add/remove packages, just redeploy:
```{r}
setwd("/Users/david/Desktop/immgenT_Apps/")
rsconnect::deployApp(appDir = "immgenT_App1", appName = "immgenT_App1")
renv::status()
rsconnect::writeManifest("immgenT_App1")
```


Sanity checks:
```{r}
renv::status() #Is your lockfile out of sync?
rsconnect::writeManifest("immgenT_App1") #Look for "appMode": "shinyapp".


```





